---
title: "6. Description of Data Layers"
toc: true
---

# Description of data layers

### Tables describing data layers (Table 7.1) and sources (Table 7.2)

**Table 7.1. Data layers of `r assessmentYear` global OHI assessment**
A brief overview of all the data layers used to calculate the global OHI.  The "Data layer" variable provides links to a full description of the data layer.  The "Description" variable provides link/s to the data preparation scripts (when available).   See Table 7.2 for a description of the data sources used to create these data layers.

```{r DataLayer Table, echo=FALSE, warning=FALSE, error=FALSE, messages=FALSE}
options(dplyr.summarise.inform=F)
## Get list of layers, name, description:
base <- read.csv(here("metadata_documentation/layers_eez_base.csv")) %>%
  # mutate(Name = paste0("[", name, "](", "http://ohi-science.org/ohi-global/layers#", layer, ")")) %>%
  select(layer, Name = name, Description = description)

## Get dimension/targets
target <- read.csv(here("metadata_documentation/layers_eez_targets.csv"), stringsAsFactors = FALSE) %>%
  mutate(goal = ifelse(dimension %in% c("pressure", "resilience", "spatial", "weighting"), dimension, goal)) %>%
  select(layer, goal) %>%
    unique() %>%
  group_by(layer) %>%
  summarize(Dimension = paste(goal, collapse = ", "))

# setdiff(base$layer, target$layer) # the sp_alien_species ends up not being used
# setdiff(target$layer, base$layer)

data <- left_join(target, base, by="layer")

## Get data prep url (will be a link in description)
url <- read.csv(here("metadata_documentation/layers_eez_dataprep.csv")) %>%
  group_by(layer) %>%
  mutate(N = 1) %>%
  mutate(method_count = cumsum(N)) %>%
  mutate(total_methods = sum(N)) %>%
  mutate(count = sum(N)) %>%
  mutate(url_link = ifelse(count==1,  sprintf("[data prep](http://ohi-science.org/ohiprep_v%s/%s)", assessmentYear, dataprep_url), 
                sprintf("[data prep %s](http://ohi-science.org/ohiprep_v%s/%s)", method_count, assessmentYear, dataprep_url))) %>%
  summarize(url_link = paste(url_link, collapse = ", ")) %>%
  select(layer, url_link) %>%
  ungroup()

data <- left_join(data, url, by="layer") %>%
  mutate(Description = sprintf("%s (%s)", Description, url_link)) %>%
  select(layer, Name, Description, Dimension)

## get references:
refs <- read.csv(here("metadata_documentation/layers_eez_reference.csv")) %>%
  select(layer, reference) %>%
  unique() %>%
  mutate(ref = paste0("@", reference)) %>%
  group_by(layer) %>%
  summarize(reference = paste(ref, collapse = "; ")) %>%
  ungroup() %>%
  #mutate(reference = paste0("[", reference, "]")) %>%
  select(layer, References=reference)
  
# setdiff(data$layer, refs$layer) # these are reasonable layers to not have references

data <- data %>%
  left_join(refs, by="layer")

### Get method updates
updates <- read.csv(here("metadata_documentation/layers_eez_updates.csv")) %>%
  select(layer, Updates=updates) %>%
  unique()

data <- data %>%
  left_join(updates, by="layer") %>%
  select(-layer) %>%
  select(Layer=Name, Description, Dimension, References, Updates) %>%
  arrange(Dimension)

kable(data) %>%
  kableExtra::kable_styling(full_width = F)

```

<br/> 

**Table 7.2. Data sources used to create data layers for `r assessmentYear` global OHI assessment**
A brief overview of the data sources used to calculate the global OHI.

```{r DataSources Table, echo=FALSE, warning=FALSE, error=FALSE, messages=FALSE}

### Get datasource primary data


## get source data
ds_source <- read.csv(here("metadata_documentation/layers_eez_data_sources.csv")) %>%
  mutate(ds_reference = paste0("@", ds_reference)) %>%
  select(Reference = ds_reference, "Description" = ds_description, Years=ds_years, Resolution = ds_native_resolution, Updated = sprintf("ds_updated_%s", assessmentYear))
kable(ds_source) %>%
  kableExtra::kable_styling(full_width = F)

```



```{r child = 'layers_all.Rmd'}
## Need to run CombineLayers.R to create the relevant Rmd file
# 'https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/documents/methods/layers_all.Rmd'
```
