---
title: "Description of Data Layers"
bibliography: ../references.bib
toc: true
callout-icon: false
callout-appearance: minimal
---

### Tables describing data layers (Table 7.1) and sources (Table 7.2)

**Table 7.1. Data layers of 2023 global OHI assessment**
A brief overview of all the data layers used to calculate the global OHI.  The "Data layer" variable provides links to a full description of the data layer.  The "Description" variable provides link/s to the data preparation scripts (when available).   See Table 7.2 for a description of the data sources used to create these data layers.

```{r, include=FALSE}
library(tidyverse)
library(magrittr)
library(kableExtra)
```

::: {.callout-note collapse=true}
### Table 7.1. Data layers of 2023 global OHI assessment (click to expand)
```{r DataLayer Table, echo=FALSE, warning=FALSE, error=FALSE, messages=FALSE}

assessmentYear <- 2024

options(dplyr.summarise.inform=F)
## Get list of layers, name, description:
base <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/76634d93f7fbc2470a2144793d15924d55f552ff/metadata_documentation/layers_eez_base.csv") %>%
  # mutate(Name = paste0("[", name, "](", "http://ohi-science.org/ohi-global/layers#", layer, ")")) %>%
  select(layer, Name = name, Description = description)

## Get dimension/targets
target <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/76634d93f7fbc2470a2144793d15924d55f552ff/metadata_documentation/layers_eez_targets.csv", stringsAsFactors = FALSE) %>%
  mutate(goal = ifelse(dimension %in% c("pressure", "resilience", "spatial", "weighting"), dimension, goal)) %>%
  select(layer, goal) %>%
    unique() %>%
  group_by(layer) %>%
  summarize(Dimension = paste(goal, collapse = ", "))

# setdiff(base$layer, target$layer) # the "sp_alien_species" and "hab_softbottom_extent" ends up not being used
# setdiff(target$layer, base$layer) # character(0)

data <- left_join(target, base, by="layer")

## Get data prep url (will be a link in description)
url <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/76634d93f7fbc2470a2144793d15924d55f552ff/metadata_documentation/layers_eez_dataprep.csv") %>%
  group_by(layer) %>%
  mutate(N = 1) %>%
  mutate(method_count = cumsum(N)) %>%
  mutate(total_methods = sum(N)) %>%
  mutate(count = sum(N)) %>%
  mutate(url_link = ifelse(count==1,  sprintf("[data prep](http://ohi-science.org/ohiprep_v%s/%s)", assessmentYear, dataprep_url), 
                sprintf("[data prep %s](http://ohi-science.org/ohiprep_v%s/%s)", method_count, assessmentYear, dataprep_url))) %>%
  summarize(url_link = paste(url_link, collapse = ", ")) %>%
  select(layer, url_link) %>%
  ungroup()

data <- left_join(data, url, by="layer") %>%
  mutate(Description = sprintf("%s (%s)", Description, url_link)) %>%
  select(layer, Name, Description, Dimension)

## get references:
refs <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/76634d93f7fbc2470a2144793d15924d55f552ff/metadata_documentation/layers_eez_reference.csv") %>%
  select(layer, reference) %>%
  unique() %>%
  mutate(ref = paste0("@", reference)) %>%
  group_by(layer) %>%
  summarize(reference = paste(ref, collapse = "; ")) %>%
  ungroup() %>%
  #mutate(reference = paste0("[", reference, "]")) %>%
  select(layer, References=reference)
  
# setdiff(data$layer, refs$layer) # "element_wts_hab_pres_abs" "uninhabited"- these are reasonable layers to not have references

data <- data %>%
  left_join(refs, by="layer")

### Get method updates
updates <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/76634d93f7fbc2470a2144793d15924d55f552ff/metadata_documentation/layers_eez_updates.csv") %>%
  select(layer, Updates=updates) %>%
  unique()

data <- data %>%
  left_join(updates, by="layer") %>%
  select(-layer) %>%
  select(Layer=Name, Description, Dimension, References, Updates) %>%
  arrange(Dimension)

kable(data) %>%
  kableExtra::kable_styling(full_width = F)
```
:::


**Table 7.2. Data sources used to create data layers for `r assessmentYear` global OHI assessment**
A brief overview of the data sources used to calculate the global OHI.

::: {.callout-note collapse=true}
### Table 7.2. Data sources used to create data layers (click to expand)
```{r DataSources Table, echo=FALSE, warning=FALSE, error=FALSE, messages=FALSE}

### Get datasource primary data

## get source data
ds_source <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/76634d93f7fbc2470a2144793d15924d55f552ff/metadata_documentation/layers_eez_data_sources.csv") %>%
  mutate(ds_reference = paste0("@", ds_reference)) %>%
  select(Reference = ds_reference, "Description" = ds_description, Years=ds_years, Resolution = ds_native_resolution, Updated = sprintf("ds_updated_%s", assessmentYear - 1))

# made it work by going up to 2023, ensure this is updated for 2024!!

kable(ds_source) %>%
  kableExtra::kable_styling(full_width = F)
```
:::


# RETURN TO THIS!
<!-- {r child = 'layers_all.Rmd'} -->
<!-- ## Need to run CombineLayers.R to create the relevant Rmd file -->
<!-- # 'https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/documents/methods/layers_all.Rmd' -->


Notes for continuing this work: 

- consider making this into 2 sections with the first 2 tables in the first section and the veeeeery long github user content (all layers Rmd) as the second section (it's extremely long... like super long and could be frustrating for users). 

- look into formatting of long tables in Quarto websites (currently annoying to scroll to the side to read the full width of the long table -- see Table 7.1) -- floating/hover (not anchored to the bottom) scroll bar (horizontal scroll bar)

- make a section of which data layers apply to which goals -- like Table 7.1, maybe just edit it so Dimension (goal/subgoal) is before description?

- consider renaming tables (current names not awesome)

- try reading in the githubuser content (even though it's super long, could be good to just see what it looks like...)

## References
